|

### 2024-10-28 output/seminar-slideshow.qmd
Version progress point

::: column
```{r mdisc-item}
#| fig-width:  4
#| fig-height: 4
mirt_item_coords |>
  arrange(desc(item))   |> # To plot them in reverse order
  ggplot(
    aes(
      0, 0,
      xend = end_transf_1 - origin_transf_1,
      yend = end_transf_2 - origin_transf_2,
      color = factor(item), fill = factor(item)
    ),
  )                                                  +
  geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
  geom_hline(yintercept = 0, linewidth = LINE_WIDTH) +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  ) +
  scale_x_continuous(
    limits       = c(-1, 2),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_y_continuous(
    limits       = c(-1, 2),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_color_manual(values = unname(PALETTE_BLUE["normal"]), guide = NULL) +
  coord_fixed(expand = FALSE, clip = "on")           +
  theme(
    axis.line        = element_blank(),
    panel.grid.major = element_line(
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```
:::
:::::

>>>>

::: column
```{r mdisc-item}
#| fig-width:  4
#| fig-height: 4
mirt_item_coords |>
  arrange(desc(item))   |> # To plot them in reverse order
  ggplot(
    aes(
      0, 0,
      xend = end_transf_1 - origin_transf_1,
      yend = end_transf_2 - origin_transf_2,
      color = factor(item), fill = factor(item)
    ),
  )                                                  +
  geom_vline(xintercept = 0, linewidth = LINE_WIDTH) +
  geom_hline(yintercept = 0, linewidth = LINE_WIDTH) +
  geom_segment(
    arrow     = arrow(angle = 20, length = unit(10, "points"), type = "closed"),
    linejoin  = "mitre",
    linewidth = VECTOR_WIDTH
  ) +
  scale_x_continuous(
    limits       = c(-1, 2), ## TODO: Change limits
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_y_continuous(
    limits       = c(-1, 2),
    breaks       = -1:2,
    minor_breaks = NULL,
    name         = NULL,
    oob          = oob_keep
  ) +
  scale_color_manual(values = unname(PALETTE_BLUE["normal"]), guide = NULL) +
  coord_fixed(expand = FALSE, clip = "on")           +
  theme(
    axis.line        = element_blank(),
    panel.grid.major = element_line(
      linewidth = LINE_WIDTH,
      linetype  = "17"
    )
  )
```
:::
:::::
